---
title: "Customer sales report"
subtitle: "mySQL | Rmarkdown"
author: "Hampus Nordholm"
date: "2024-12-02"
output:
  pdf_document:
    latex_engine: xelatex
    
---

```{r,message=FALSE,warning=FALSE,echo=FALSE}
#LIBRARY -- 
library(tidyverse)
```


```{r,message=FALSE,warning=FALSE,echo=FALSE}
#Loading CSV:s exportedfrom mySQL -- 

ch_tbl <- read_csv("custchurn.csv")

top10_tbl <- read_csv("toptencust.csv")

```

# Background 

The insights presented in this report were extracted from a MySQL database containing  customer transaction data. The primary objective of this analysis was to identify high-risk customers, those with an average time between orders greater than 365 days and to report the most profitable customers for the business. 

# Insights 

## High risk customers 

```{r,echo=FALSE}
#GGplot highrisk.vs loyal 
ch_tbl %>% 
  ggplot(aes(customer_status,total_customers,fill=customer_status))+
  geom_col()+
  labs(y="Total customers",x=NULL)

#Numbers table-- 
ch_tbl


```

The chart above shows the distribution of customers by their status (number of high-risk versus loyal customers). As shown there are 251 high-risk customers, with an average time between orders of 409 days, and 1,194 loyal customers, with an average time between orders of 199 days.

## Top 10 customers by revenue 
The barchart below displays the top 10 customers ranked by total revenue in descending order, followed by a list of their names, revenue, total orders and latest order date.

```{r,echo=FALSE}
#GGplot barchart -- 
top10_tbl %>%
  ggplot(aes(revenue,reorder(fullname, revenue),fill=revenue)) +  
  geom_col()+
  labs(x="Revenue(USD)",y="Name")+
  theme(legend.position="none")

```

## Top 10 customers table 
```{r,echo=FALSE}
#Table --
top10_tbl

```





